% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[resmargin]{res}
\usepackage[margin=0.5in]{geometry}
%\topmargin=-0.8in
%\oddsidemargin -.5in
%\evensidemargin -.5in
\textwidth=6.1in % increase textwidth to get smaller right margin
%\itemsep=0in
%\parsep=0in
% the margin option causes section titles to appear to the left of body text 
%\newsectionwidth{27.5pt}
%\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 


\begin{document} 
 
\name{\huge SOO-YEON VERONICA SEO \\ [12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bfseries Present Address} \\ 329L Undergraduate Hall 6 HKUST \\ Clear Water Bay \\ Hong Kong \\ }
\address{{\bfseries Contact Details} \\ +852 6882 9425 \\ syseo@connect.ust.hk \\ linkedin.com/in/veronicasyseo }

 
\begin{resume} 
 
% \section{Objective} 
% Auditing/Analysis of Operations 

\section{Education}
{\bf The Hong Kong University of Science and Technology} \hfill \textit{2013 - December 2017} \\
Bachelor of Engineering in Industrial Engineering and Engineering Management
\begin{itemize} \itemsep -2pt %reduce space between items
\item Expected Second Class Honors Division 1 (2:1) with Minor in Business
\item Relevant Coursework: FinTech Consulting; Intermediate Corporate Finance and Investments; Corporate Valuation; Quantitative Methods in Financial Engineering
\end{itemize}
 

\section{Experience}
{\bf Student Mentor,} Department of Industrial Engineering at HKUST \hfill \textit{Spring 2017}
\begin{itemize} \itemsep -2pt % adjust line spacing
\item Undergraduate TA for the course \textit{Experiential Computing in Industrial Applications}.
\item The course is one of the University's first self-directed and experiential learning modules.
\end{itemize}

 {\bf Research Intern,} Entopsis Hong Kong \hfill \textit{Summer 2016}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Conducted in-depth industry research and due diligence of listed Chinese companies in the health care sector to form the basis for the firm's first biotech investment fund, with a focus on researching potential investment targets.
 \item Extensively used Excel and Bloomberg to create and maintain a database.
 \item Wrote and presented analyses on emerging technologies, in particular blockchain and smart contracts in insurance applications, to various stakeholders.
 \end{itemize} % really sell them that I'm worth something in this area and milk down what i did to the essence and how did i help with the firm in the end

%
{\bf Semester Student Consultant,} IBM Global Business Services Hong Kong \hfill \textit{Fall 2015}
\begin{itemize} \itemsep -2pt
\item Led a team of five Engineering and Risk Management student consultants to develop market strategies for a peer-to-peer real estate crowdfunding startup.
% Self-initiated activities included: cold-calling commercial banks to negotiate loan rates; learning the Chinese P2P lending landscape through firm visits;
\item Conducted 70+ in-person and on-line investor sentiment surveys, then presented analyses of the findings to instructors and IBM mentors.
\item Final presentation of three short- and medium-term strategies was awarded Judges' Favorite and deemed the most implementable and highest-impact out of those presented.
\end{itemize} % say more about the different things our team did to differentiate. also how i made an impact by leading the team
% how did i lead the team for the second consulting project? how were we selected? mention self directed learning and reflection and how it was a chance to integrate classroom theories into real hands on practice to derive value. also mention project management tools used / learned

%
{\bf Business Intern,} Tink Labs Hong Kong \hfill  \textit{Summer 2015}
\begin{itemize} \itemsep -2pt %reduce space between items
\item Rotated among all core departments to monitor analytics and measure customer sentiment. Using insights gathered from sentiment analysis, updated and generated Chinese and English content, which was then uploaded onto firm's product.
\item Ran on-site troubleshooting missions on a near-daily basis and instructed hotel staff on software maintenance and update protocol. Often used tools included: Salesforce, Excel, proprietary content management software.
\end{itemize} % what did i do of value to the firm? what skills did i utilize and learn - for example cold-calling? did i resolve disputes? how did bottom line etc. other quantitative markers during my time there positively change as a result of my actions?

%
\section{Leadership \\ Activities} 
    {\bf Lead Organizer,} Hackathon at HKUST (HackUST) \hfill \textit{September 2015 - present}
        \begin{itemize} \itemsep -2pt
        \item Oversee sponsorships and spearhead media coverage of the event to ultimately increase participant turnout twofold, from 220 in 2015 to 400 in 2016. 
        \item Liaise with local and international mentors and judges. Promote maker culture through organizing workshops and by publishing content on social media to build an inclusive community.
		 \end{itemize}
         % emphasis on my efforts to build a community and tech evangelism roles, e.g. writing on facebook groups, blogs
         % why do i do this? to promote entrepreneurial culture in UST where there isn't too much of it. how do i make the most impact? where did i oversee? did i direct volunteers? budgeting? sponsor engagements? bring in speakers? bring in mentors?


\section{Honors and \\ Awards} 
Hackathons: {\bf Best Use of BlackRock Aladdin API,} MHacks 8 at the University of Michigan, Fall 2016. {\bf Regional Champion,} Fishackathon Hong Kong sponsored by the U.S. Department of State and the Hong Kong Government, Spring 2016. % what role do i play at hackathons? why do i attend hackathons? what are some of the projects that i've created? what do they say about me and my aims and the kind of people i work with? what role do i play on-line in hacker communities?


% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Additional \\ Information}
    Languages: Heritage: Korean and Mandarin Chinese, Basic: Cantonese \\
    Computer Skills: Excel, Bloomberg, Minitab, R, Python, Git, \LaTeX, basic Java and Matlab \\
    Certifications: HSK Level 6 (2011), Six Sigma Green Belt (2017) \\
    Interests: Financial technology, sociology, travel, active hackathon hacker \\
    % what do my interests reveal about me? what connections, if any, do they have to who i am professionally? if they do not, should they be on this list? what do i really enjoy doing outside of work and study?


\end{resume} 
\end{document} 